	\begin{abstract} Entity alignment - establishing the link between two entities across entity corpus - is an important task for natural
language processing. This task is typically performed on the knowledge graphs (\KGs) by using graph embedding methods to represent entities
and their context. However, existing approaches often fail to identify the spares but discriminative evidence from heterogenous \KGs that
typically have different structures and properties. As a result, exiting entity alignment methods either have to rely on strong assumptions
which are difficult to satisfy or deliver poor performance. Our work introduces a better way for entity alignment. We employ the relational
graph convolutional network to better characterize entities by incorporating the neighboring relational structures and the entity semantic
and attribute information. Further, we show that by introducing layer-wise highway network gates to the network, our approach can
effectively filter out the propagation of noisy information to ensure the quality of the learning. Experiments performed on two real-world
datasets show that our approach outperforms prior methods but using less alignment information.

		%Entity alignment is the task of linking entities and their counterparts among multiple knowledge graphs (\KGs).
%		Most recent works rely on knowledge graph embedding methods, such as TransE, to represent entities and their context, which often have difficulties in identifying sparse but discriminative evidence, utilizing attribute values and dealing with unbalanced neighboring context.
%		To address these issues, we present RGCN, a novel entity alignment model which leverages relational graph convolutional networks to better characterize entities by incorporating the neighboring relational structure information and taking attribute values into account.
%		We further introduce layer-wise highway network gates to filter out the propagation of noisy information and ensure effective spread of more informative and discriminative neighborhood information.
%		Experiments on real-world datasets show that our approach further improves entity alignment performance on various \KGs, and gets the best performance compared with competitive baselines.
	\end{abstract}
