\section{Motivation}
As a motivation example, consider Figure~\ref{Xinjiang} which depicts \FIXME{three} heterogeneous \KGs extracted from the Wiki and Baidu
datasets (see Section~\ref{section:datasets}). In the diagram, an entity is marked by a circle and a value is indicated by a rectangle,
while an attribute or relation is listed on the edge. \FIXME{We need three \KGs if you want to keep this example. The three \KGs should all
contain \emph{Urumqi}, but only two of them have \emph{Xinjiang} in common, i.e., we want to show that the attribute value is also needed
for entity alignment. }

The three \KGs have some entities (e.g., \emph{Urumqi}) and attributes (e.g., area) in common but their graph structure is different from
each. Specifically, \KGs 1 and 3 contain a common entity of \emph{Xinjiang} (the surface form of this entity in Wiki is \emph{Xinjiang
Uygur Autonomous Region}). Therefore, a successful entity alignment strategy needs to link \emph{Xinjiang} from both \KGs. However,
state-of-the-art entity alignment methods~\cite{hao2016joint,chen2016multilingual,sun2017cross,zhu2017iterative} built upon TransE all fail
to align this entity because of two reasons: (i) they are misled by some of the redundant entities and attributes that only appear in the
Baidu dataset and (ii) they do not utilize attributes like \emph{1,660,000$km^2$}. This is a problem when using translation-based
embedding.

If we look closely into \KGs 1 and 3, we find that the \emph{Xinjiang} entity can be aligned using the entity \emph{Urumqi} highlighted by
the blue circle together with an attribute value \emph{1,660,000$km^2$} highlighted by a green rectangle. In this example, if we can treat
other entities and attributes as noise, we can successfully align the \emph{Xinjiang} entity.

This example shows that entity alignment requires one to carefully evaluate the importance of each entity and attribute from heterogeneous
\KGs. Unfortunately, this information varies across datasets and entities. Because manually obtaining this information for every target
entity would incur significant overhead, there is a critical need to automate the process. In this paper, we describe an novel approach to
offer this capability based on the \RGCN.
